Dashboards for stock assessments: Getting started

### 2019-10-21 analysis/dashboards/getting_started.Rmd
Shift the structure of the getting_started dashboard and add a quick start tab to the skeleton page

---
title: "Dashboards for stock assessments: Getting started"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    source_code: embed
---

@@

rmarkdown {data-navmenu="Basics"}
=======================================================================

@@

flexdashboard {data-navmenu="Basics"}
=======================================================================

@@

plotly {data-navmenu="Basics" data-orientation=columns}
=======================================================================

@@

crosstalk {data-navmenu="Basics" data-orientation=columns}
=======================================================================

>>>>

---
title: "Dashboards for stock assessments: Getting started"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
---

@@

TEMP {.hidden}
=======================================================================

```{r, eval = TRUE, include=FALSE}
leaflet::leaflet() # subsequent leaflet would not render withouth an eariler call to leaflet for some unknown reason?
```

### Quick start

**1\.** `r xfun::embed_files(c("skeleton.Rmd", "length-weight_data.csv"), text = "Download code and data")`

**2\.** Open `skeleton.Rmd` in Rstudio

**3\.** Install packages: `install.packages(c("flexdashboard", "plotly", "crosstalk"))`

**4\.** Knit file by typing `Ctrl+Shift+K` or use the `r knitr::include_graphics("knit_button.png", dpi = 175)` button

rmarkdown {data-navmenu="Extra"}
=======================================================================

@@

flexdashboard {data-navmenu="Extra"}
=======================================================================

@@

plotly {data-navmenu="Extra" data-orientation=columns}
=======================================================================

@@

crosstalk {data-navmenu="Extra" data-orientation=columns}
=======================================================================
